Formalizing Stack Safety as a Security Property

### 2022-11-15 submission5/noexceptions.tex
Fixing diagrams
Update to comments

\usepackage{multirow}

@@

%  Every security-relevant operation manipulates the call stack via a function
%\(Op : \MACHS \rightarrow \CONTEXTS \rightarrow \psi \rightarrow \CONTEXTS\).

%From a machine state and a context, we create a {\it combined state}
%\(s = (\mach,\context)\) and a transition \(\stepstounder{}\) on combined states,
%labeled with the same operations. Note that \(Op\) takes as its state argument
%\(\mach\), the state before the step.

%\judgmenttwo{\(\mach \xrightarrow{\overline{\psi}} \mach', \obs \)}
%            {\(\mathit{foldl} ~ (Op ~ \mach) ~ \context ~ \overline{\psi} = \context'\)}
%            {\((\mach,\context) \stepstounder{\overline{\psi}} (\mach', \context', \obs)\)}

%\subsection{Policy State}

%\apt{As we discussed at length, it would certainly be nice to avoid separate policy state if possible.}
%In addition to its elements, a system may contain additional ``policy'' state that carries
%information relevant to a hardware enforcement mechanism. We assume that policy state
%cannot influence execution, except possibly to cause the system to failstop, which is modeled
%as a state stepping to itself. A failstop is therefore indistinguishable from silent
%divergence.

%Formally, we can treat our machine state as
%\(\mach = (\mach[\cdot],\langle \mach \rangle) \in \MACHS
%::= (\COMPONENTS \rightarrow \WORDS) \times \POLS\) for some \(\POLS\).
%\apt{This overloaded notation doesn't work. $\mach$ can be either a pair or a map, not both.
%Note that earlier text strongly implies that it is a map.}
%Then \(\langle \mach \rangle\) is the security state. We assume that if
%\(\mach[\component] = \nach[\component]\) for all \(\component\),
%%\(\mach \stepstounder{\bar{\psi_1}} \mach'\), and \(\nach \stepstounder{\bar{\psi_2}} \nach'\),
%then \(\bar{\psi_1} = \bar{\psi_2}\) and either
%\(\mach = \mach'\), \(\nach = \nach'\), or \(\mach'[\component] = \nach'[\component]\)
%for all \(\component\).

@@

\begin{figure*}
  \begin{subfigure}[t]{.55\textwidth}
    \vskip 0pt
    \begin{tabular}{|r|r||l|}
      \hline
      \(\PCname\) & \(\SP\) & Context \\
      \hline
      0 & 1000 & \(V_0, \emplist\) \\
      \hline
      \multicolumn{3}{l}{\(1 \downarrow [\mathbf{alloc} ~ (-20,20)]\)} \\
      \hline
      4 & 980 & \(V_1 = V_0 \llbracket 980..999 \mapsto \object\rrbracket, \emplist\) \\
      \hline
      \multicolumn{3}{l}{\(2 \downarrow []\)} \\
      \multicolumn{3}{l}{\(\ \ \vdots\)} \\
      \multicolumn{3}{l}{\(4 \downarrow []\)} \\
      \hline
      16 & 980 & \(V_1, \emplist\) \\
      \hline
      \multicolumn{3}{l}{\(5 \downarrow [\mathbf{call} ~ 100 ~ \emplist ~ \emplist]\)} \\
      \hline
      100 & 980 & \(V_2 = V_1 \llbracket 980..999 \mapsto \sealed, \mathtt{a0} \mapsto \unsealed\rrbracket,[V_1]\) \\
      \hline
      \multicolumn{3}{l}{\(6 \downarrow []\)} \\
      \multicolumn{3}{l}{\(\ \ \vdots\)} \\
      \multicolumn{3}{l}{\(8 \downarrow []\)} \\
      \hline
      112 & 980 & \(V_2,[V_1]\) \\
      \hline
      \multicolumn{3}{l}{\(9 \downarrow [\mathbf{return}]\)} \\
      \hline
      20 & 980  & \(V_1, \emplist\) \\
      \hline
    \end{tabular}
  \end{subfigure}
  \begin{subfigure}[t]{.4\textwidth}
    \vskip 0px

    \(\underbrace{~ ~ ~}_\unsealed \uparrow \SP \)

    \includegraphics[width=\columnwidth]{stack2.png}
    \includegraphics[width=\columnwidth]{stack3.png}
    \includegraphics[width=\columnwidth]{stack4.png}
  \end{subfigure}

\caption{Execution up through the return from {\tt f}\apt{Label rows on right. Also show registers?}}
\label{fig:exec1}
\end{figure*}
%
At step 5, the formerly active principal's record is pushed onto the inactive list.
Its return target is the return address of the call, 
and the stack pointer target is the stack pointer at the moment of call.
The callee's view is updated from the caller's such that all \(\object\) locations
become \(\sealed\). (In more complex settings, objects that are intentionally passed
to the callee will not get sealed, but for now we assume no sharing of memory between activations.)
For registers, \(\overline{\reg_{args}}\) tells us which registers are used as arguments,
in this case just {\tt a0}. These are mapped to \(\public\), while any non-argument, caller-saved
registers remain mapped to \(\unsealed\). All callee-save registers remain \(\sealed\) for all calls.
At step 9, {\tt f} returns, and the topmost inactive view, that of {\tt main}, is restored.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{variants2.png}
  \caption{Internal Confidentiality Violation\apt{needs key cells to be colored}}
  \label{fig:variant2}
\end{figure}

@@

In place of a predicate we define \(\conf\) as a binary relation on states, 
which holds on eventual return states \((\mach',\context')\) and
\((\nach',\context'')\)
iff all relevant elements that changed between \(\mach\) and \(\mach'\) or \(\nach\) and \(\nach'\)
are the same in \(\mach\) and \(\nach\). We then define
return-time confidentiality as holding if \(\conf\) holds on the matching return states
from \(\mach\) and \(\nach\), respectively.

@@

\section{Events and Traces}
\label{sec:events}

@@

\section{Facts Abouts Calls and Returns}
\label{sec:facts}

@@

\section{Properties}
\label{sec:props}

We now finally have everything we need to formalize our definitions for stack safety.
Figure \ref{fig:oprules} gives the operation rules for all of the operations we've described
so far.

\begin{figure}

  \judgmentbr[Call]
             {\(\psi = \mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa}\)}
             {\(V' = V \llbracket \reg \mapsto \unsealed | \reg \in \mathit{CLR} \rrbracket
               \llbracket \reg \mapsto \public | \reg \in \overline{\reg_{args}} \rrbracket\)}
             {\(Op ~ \mach ~ \psi ~ (V,\sigma) =
               (V',V::\sigma)\)}

%\judgment[RetDef]
%         {\(\chi = \mathbf{return}\)}
%         {\(Cop ~ \chi ~ (V, \emplist) ~ \mach \triangleq
%           (V, \emplist)\)}

  \caption{Core operation rules for the simple system}
  \label{fig:oprules}
\end{figure}

\subsection{Well-bracketed Control Flow}

@@

\subsection{Integrity}

@@

\subsection{Caller Confidentiality}

@@

\subsection{Callee Confidentiality}

@@

The advanced machine defines additional operations, and adds a field \(\overline{sa}\) to
the \(\mathbf{call}\) operation, which is a set of triples of a register, a base offset, and a size,
and denotes that the object at the offset from the given register is to be passed as an argument.

\begin{align*}
  \psi \in \Psi ::= & \mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa} &
  sa \in \REGS \times \mathbb{Z} \times \mathbb{N} \\
  | & \mathbf{tailcall} ~ \addr_{target}  ~ \overline{\reg_{args}} ~ \overline{sa} &
  sa \in \REGS \times \mathbb{Z} \times \mathbb{N} \\
  | & \mathbf{return} & \\
  | & \mathbf{alloc} ~ \mathit{off ~ sz} & \mathit{off, sz} \in \mathbb{N} \\
  | & \mathbf{dealloc} ~ \mathit{off ~ sz} & \mathit{off, sz} \in \mathbb{N} \\
\end{align*}

%We can extend our basic machine to support public memory allocations that can
%be accessed by anyone until they are deallocated on their owner's return,
%using the \(\mathbf{alloc\_pub}\) operation. This behaves identically to
%\(\mathbf{alloc\_priv}\) except that it marks the locations \(\public\).
%For example, consider the following code:

%{\tt
%  void g() \{

%  ~ ~ int x[3];

%  ~ ~ int y;

%  ~ ~ h(\&x);

%  \}
%}

%Here we have allocated several arrays and variables; {\tt y}
%will behave as normal with \(\mathit{alloc\_priv}\), but {\tt x} has its
%address taken and passed to another function. That function might do anything at
%all to {\tt x}, and we have to decide whether it can be said to violate stack
%safety. A reasonable default is to assume that any address-taken local should be
%public, while {\tt y} is still private.

%In the likely event that the space for the return address, {\tt x}, and {\tt y}
%are all allocated in a single step, that step needs multiple labels to capture
%that they are not all private. Its label would instead be:
%\[\begin{split}
%& \psi = [\mathbf{alloc\_priv} ~ (20,4); \\
%  & \mathbf{alloc\_pub} ~ (16,12) ; \mathbf{alloc\_priv} ~ (4,4)]
%\end{split}\]

%Allocating public objects affects the call stack very similarly to private ones,
%but instead of treating them as \(\sealed\) they become \(\public\). This makes these
%regions of memory able to transmit information between caller and callee without
%violating the stack safety properties. Note that there is no way to seal a location
%once it has become \(\public\); only when {\tt g} returns will the memory allocated
%to {\tt x} be available for private use.

%\judgmentbr{\(b = \mach[\SP] - \mathit{off}\)}
%           {\(V' = V \llbracket \addr \mapsto \public |
%             b \leq a < b+\mathit{sz} \land V ~ \addr = \unsealed \rrbracket\)}
%           {\(Pop ~ (\mathbf{alloc\_pub} ~ \mathit{off, sz}) ~ (V,\sigma) ~ \mach \triangleq
%             (V',\sigma)\)}

@@

So we must refine our call operation to make use of the information that we have about
which memory contain arguments, \(\overline{sa}\). \(\overline{sa}\) is a set of
triples of a register, an offset from the value of that register, and a size.
We first define the helpful set \(\mathit{passed} ~ \overline{sa} ~ \mach\),
then extend the call operation to keep all objects in \(\mathit{passed}\) marked
as \(\object\) and seal everything else.
%
\[\mathit{passed} ~ \overline{sa} ~ \mach \triangleq
\bigcup_{(\reg,b,o) \in \overline{sa}} \{\mach[\reg]+i | b \leq i < b+o\}\]
%
\judgmentbrbr[]
             {\(\psi = \mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa}\)}
             {\(V' = V \llbracket \reg \mapsto \unsealed | \reg \in \mathit{CLR} \rrbracket
               \llbracket \reg \mapsto \public | \reg \in \overline{\reg_{args}} \rrbracket\)}
             {\(V'' = V'\llbracket \addr \mapsto \sealed | V' ~ \addr = \object \land \addr \not \in (\mathit{passed} ~ \overline{sa} ~ \mach) \rrbracket\)}
             {\(Op ~ \mach ~ \psi ~ (V,\sigma) =
               (V',V::\sigma)\)}

@@

This same structure works for pass-by-reference arguments: we know from the type of
the called function which register it expects to hold the address of a given object,
and the size of that object. In this case the offset will always be 0.

When the callee in such a scenario makes a call of its own, the objects passed to it
will in turn be sealed---unless it passes them on, which can happen with pass-by-reference
arguments!

@@

State beyond registers and memory is always considered \(\public\), and in a PIPE machine this
includes tags. That does not mean that functions should be modifying them! It just means that we
do not consider them to be part of the state being protected. It is less obvious that a function
should be prevented reading a tag, and our properties do not rule it out, although in practice
PIPE does not allow such reads.

>>>>

\usepackage{array,multirow}

@@

@@

\newcommand{\freebox}{\includegraphics[height=10px]{free.png}}
\newcommand{\pubbox}{\includegraphics[height=10px]{public.png}}
\newcommand{\objbox}{\includegraphics[height=10px]{object.png}}
\newcommand{\sealbox}{\includegraphics[height=10px]{sealed.png}}

\begin{figure*}
  \begin{tabular}{|r|r||l|r}
    \cline{1-3}
    \(\PCname\) & \(\SP\) & Context &
    \multirow{3}{*}{\(\underbrace{\dots \freebox \freebox \freebox \freebox \freebox
        \freebox \freebox \freebox \freebox \freebox}_\unsealed
      \! \underbrace{\stackrel{\stackrel{\SP}{\downarrow}}{\pubbox} \!\! \pubbox \pubbox \dots}_\public
      ~ \stackrel{\mathtt{a1}}{\pubbox} ~ \stackrel{\mathtt{a2}}{\freebox}
      ~ \stackrel{\mathtt{s0}}{\sealbox}
      \)} \\
    \cline{1-3}
    0 & 1000 & \(V_0, \emplist\)
    \\
    \cline{1-3}
    \multicolumn{3}{l}{\multirow{2}{*}{\(1 \Big\downarrow [\mathbf{alloc} ~ (-20,20)]\)}} & \\
    \multicolumn{3}{l}{} &
    \multirow{3}{*}{\(\underbrace{\dots \freebox \freebox \freebox \freebox \freebox}_\unsealed
      \! \underbrace{\stackrel{\stackrel{\SP}{\downarrow}}{\objbox} \!\! \objbox \objbox \objbox \objbox}_\object
      \! \underbrace{\pubbox \pubbox \pubbox \dots}_\public
      ~ \stackrel{\mathtt{a1}}{\pubbox} ~ \stackrel{\mathtt{a2}}{\freebox}
      ~ \stackrel{\mathtt{s0}}{\sealbox}
      \)}
    \\
    \cline{1-3}
    4 & 980 & \(V_1 = V_0 \llbracket 980..999 \mapsto \object\rrbracket, \emplist\) &
    \\
    \cline{1-3}
    \multicolumn{3}{l}{\multirow{2}{*}{2-4 \(\Big\downarrow \emplist\)}} \\ \multicolumn{3}{l}{} \\
    \cline{1-3}
    16 & 980 & \(V_1, \emplist\) & \\
    \cline{1-3}
    \multicolumn{3}{l}{\multirow{2}{*}{\(5 \Big\downarrow [\mathbf{call} ~ 100 ~ \emplist]\)}} & \\
    \multicolumn{3}{l}{} &
    \multirow{3}{*}{\(\underbrace{\dots \freebox \freebox \freebox \freebox \freebox}_\unsealed
      \! \underbrace{\stackrel{\stackrel{\SP}{\downarrow}}{\sealbox} \!\! \sealbox \sealbox \sealbox \sealbox}_\sealed
      \! \underbrace{\pubbox \pubbox \pubbox \dots}_\public
      ~ \stackrel{\mathtt{a1}}{\freebox} ~ \stackrel{\mathtt{a2}}{\freebox}
      ~ \stackrel{\mathtt{s0}}{\sealbox}
      \)}
    \\
    \cline{1-3}
    100 & 980 & \(V_2 = V_1 \llbracket 980..999 \mapsto \sealed, \mathtt{a0} \mapsto \unsealed\rrbracket,[V_1]\) & \\
    \cline{1-3}
    \multicolumn{3}{l}{\multirow{2}{*}{6-8 \(\Big\downarrow \emplist\)}} \\ \multicolumn{3}{l}{} \\
    \cline{1-3}
    112 & 980 & \(V_2,[V_1]\) \\
    \cline{1-3}
    \multicolumn{3}{l}{\multirow{2}{*}{\(9 \Big\downarrow [\mathbf{return}]\)}} & \\
    \multicolumn{3}{l}{} & \multirow{3}{*}{\(\underbrace{\dots \freebox \freebox \freebox \freebox \freebox}_\unsealed
      \! \underbrace{\stackrel{\stackrel{\SP}{\downarrow}}{\objbox} \!\! \objbox \objbox \objbox \objbox}_\object
      \! \underbrace{\pubbox \pubbox \pubbox \dots}_\public
      ~ \stackrel{\mathtt{a1}}{\pubbox} ~ \stackrel{\mathtt{a2}}{\freebox}
      ~ \stackrel{\mathtt{s0}}{\sealbox}
      \)}
    \\
    \cline{1-3}
    20 & 980  & \(V_1, \emplist\) &
    \\
    \cline{1-3}
    \multicolumn{2}{l}{} \\
  \end{tabular}
\caption{Execution up through the return from {\tt f}}
\label{fig:exec1}
\end{figure*}
%
At step 5, the formerly active principal's record is pushed onto the inactive list.
Its return target is the return address of the call, 
and the stack pointer target is the stack pointer at the moment of call.
The callee's view is updated from the caller's such that all \(\object\) locations
become \(\sealed\). (In more complex settings, objects that are intentionally passed
to the callee will not get sealed, but for now we assume no sharing of memory between activations.)
For registers, \(\overline{\reg_{args}}\) tells us which registers are used as arguments,
in this case just {\tt a0}. These are mapped to \(\public\), while any non-argument, caller-saved
registers remain mapped to \(\unsealed\). All callee-save registers remain \(\sealed\) for all calls.
At step 9, {\tt f} returns, and the topmost inactive view, that of {\tt main}, is restored.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{variants2.png}
  \caption{Internal Confidentiality Violation}
  \label{fig:variant2}
\end{figure}

@@

In place of a predicate we define \(\conf\) as a binary relation on states, 
which holds on eventual return states \(\mach'\) and \(\nach'\)
iff all relevant elements that changed between \(\mach\) and \(\mach'\) or \(\nach\) and \(\nach'\)
are the same in \(\mach\) and \(\nach\). We then define
return-time confidentiality as holding if \(\conf\) holds on the matching return states
from \(\mach\) and \(\nach\), respectively.

@@

\section{Property Formalisms}

We have described informally how the security context develops as the system performs
security-relevant operations. Formally, we combine each machine state with a context
to create a {\it combined state} \(s = (\mach,\context)\) and a lift the transition
transition \(\stepstounder{}\) on combined states, labeled with the same operations.
with each step, the context updates based on the function
\(Op : \MACHS \rightarrow \CONTEXTS \rightarrow \psi \rightarrow \CONTEXTS\).
Note that \(Op\) takes as its first argument the state {\it before} the step.
Since a single step might correspond to multiple operations, we apply
\(Op\) as many times as is needed.

\judgmenttwo{\(\mach \xrightarrow{\overline{\psi}} \mach', \obs \)}
            {\(\mathit{foldl} ~ (Op ~ \mach) ~ \context ~ \overline{\psi} = \context'\)}
            {\((\mach,\context) \stepstounder{\overline{\psi}} (\mach', \context', \obs)\)}

The definition of \(Op\) is most convenient to present decomposed into
rules for each operation. In the simple system, the operations affect the
context as follows:

\judgmentbr[Call]
           {\(\psi = \mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}}\)}
           {\(V' = V \llbracket \reg \mapsto \unsealed | \reg \in \mathit{CLR} \rrbracket
             \llbracket \reg \mapsto \public | \reg \in \overline{\reg_{args}} \rrbracket\)}
           {\(Op ~ \mach ~ \psi ~ (V,\sigma) =
             (V',V::\sigma)\)}

\subsection{Events and Traces}
\label{sec:events}

@@

\subsection{Facts Abouts Calls and Returns}
\label{sec:facts}

@@

\subsection{Properties}
\label{sec:props}

@@

\paragraph*{Integrity}

@@

@@

@@

The advanced machine defines additional operations, and extends some of the old ones.
It adds a field \(\overline{sa}\) to the \(\mathbf{call}\) operation, which is a set of
triples of a register, a base offset, and a size, and denotes that the object at the offset
from the given register is to be passed as an argument. The new \(\mathbf{tailcall}\) operation
has the same fields, but deals with tail call optimizations in which the callee will reuse
the caller's stack. The \(\mathbf{alloc}\) operation
gains a boolen flag indicating whether the allocation is to be public, accessible to
all functions until deallocated. And, we add the corresponding \(\mathbf{dealloc}\)
operation.

\begin{align*}
  \psi \in \Psi ::= & \mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa} &
  sa \in \REGS \times \mathbb{Z} \times \mathbb{N} \\
  | & \mathbf{tailcall} ~ \addr_{target}  ~ \overline{\reg_{args}} ~ \overline{sa} &
  sa \in \REGS \times \mathbb{Z} \times \mathbb{N} \\
  | & \mathbf{return} & \\
  | & \mathbf{alloc} ~ \mathit{pub} ~ \mathit{off ~ sz} & \mathit{off, sz} \in \mathbb{N}, \mathit{pub} \in \mathbb{B} \\
  | & \mathbf{dealloc} ~ \mathit{off ~ sz} & \mathit{off, sz} \in \mathbb{N} \\
\end{align*}

\subsection{Public Allocations}

The advanced machine supports public stack allocations that can
be accessed by anyone until they are deallocated on their owner's return,
represented by \(\mathbf{alloc} ~ \mathbf{t} \dots\).
For example, consider the following code:

{\tt
  void g() \{

  ~ ~ int x[3];

  ~ ~ int y;

  ~ ~ h(\&x);

Here we have allocated several arrays and variables; {\tt y}
will behave as normal with \(\mathbf{alloc} ~ \mathbf{f} \dots\), but
{\tt x} has its address taken and passed to another function. That
function might do anything at all to {\tt x}, and might store its pointer
elsewhere (in the heap, for instance) so that the scope of legitimate accesses
to {\tt x} are uncertain. We default to assuming that any address-taken local
should be public. Meanwhile {\tt y} is still private.

In the likely event that the space for the return address, {\tt x}, and {\tt y}
are all allocated in a single step, that step makes multiple allocation operations:
\[\bar{\psi} = [\mathbf{alloc} ~ \mathbf{f} ~ (-20,4);
 \mathbf{alloc} ~ \mathbf{t} ~ (-16,12) ; \mathbf{alloc} ~ \mathbf{f} ~ (-4,4)]\]

Allocating public objects affects the call stack very similarly to private ones,
but instead of labeling them \(\object\) they become \(\public\), so they are
not sealed at a call. This makes these
regions of memory able to transmit information between caller and callee without
violating the stack safety properties. Note that there is no way to seal a location
once it has become \(\public\); only when {\tt x} is deallocated will its region
be available to allocate privately.

\judgmentbr[AllocPriv]
           {\(b = \mach[\SP] + \mathit{off}\)}
           {\(V' = V \llbracket \addr \mapsto \sealed |
             b \leq a < b+\mathit{sz} \land V ~ \addr = \unsealed \rrbracket\)}
           {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathbf{f} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}

\judgmentbr[AllocPub]
           {\(b = \mach[\SP] + \mathit{off}\)}
           {\(V' = V \llbracket \addr \mapsto \public |
             b \leq a < b+\mathit{sz} \land V ~ \addr = \unsealed \rrbracket\)}
           {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathbf{t} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}

\judgmentbr[Dealloc]
           {\(b = \mach[\SP] + \mathit{off}\)}
           {\(V' = V \llbracket \addr \mapsto \unsealed |
             b \leq a < b+\mathit{sz} \land V ~ \addr \in \{\object, \public\} \rrbracket\)}
           {\(Op ~ \mach ~ (\mathbf{dealloc} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}

@@

So we must refine our call operation to make use of the information that we have about
which memory contain arguments, \(\overline{sa}\). \(\overline{sa}\) is a set of
triples of a register, an offset from the value of that register, and a size.
We first define the helpful set \(\mathit{passed} ~ \overline{sa} ~ \mach\),
then extend the call operation to keep all objects in \(\mathit{passed}\) marked
as \(\object\) and seal everything else.
%
\[\mathit{passed} ~ \overline{sa} ~ \mach \triangleq
\bigcup_{(\reg,b,o) \in \overline{sa}} \{\mach[\reg]+i | b \leq i < b+o\}\]
%
\judgmentbrbr[]
             {\(\psi = \mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa}\)}
             {\(V' = V \llbracket \reg \mapsto \unsealed | \reg \in \mathit{CLR} \rrbracket
               \llbracket \reg \mapsto \public | \reg \in \overline{\reg_{args}} \rrbracket\)}
             {\(V'' = V'\llbracket \addr \mapsto \sealed | V' ~ \addr = \object \land \addr \not \in (\mathit{passed} ~ \overline{sa} ~ \mach) \rrbracket\)}
             {\(Op ~ \mach ~ \psi ~ (V,\sigma) =
               (V'',V::\sigma)\)}

@@

This same structure works for pass-by-reference arguments. In this case {\tt main}
passes an array {\tt x} directly, which is compiled as a pass-by-reference.

{\tt
  int main() \{

  ~ int x[1];

  ~ f(x);

  ~ g();

  ~ return x[0];

Unlike the address-taken array, we can clearly delineate the scope in which {\tt x} may be
accessed without violating stack safety: {\tt f} should be allowed to access it, but further
calls from {\tt f} should not (unless {\tt f} passes it to them) and {\tt g} certainly
should not. Say the compiler opts to pass the pointer to {\tt x} in register {\tt a0}.
The {\tt f} is specifically being given access to the four bytes starting at that address.
The call operation is \(\mathbf{call} ~ \emplist ~ \{(\mathtt{a0},0,4)\}\).

\subsection{Tailcalls}

The operation rule for a tailcall is similar to that for a normal call.
We do not push the caller's view onto the stack,
but replace it outright. This means that a tailcall does not increase the size of
the call stack, and therefore for purposes of our properties, all tailcalls will
be considered to return simultaneously when the eventual {\bf return} operation
pops the top of the stack.

Since the caller will not be returned to, it does not need integrity, though
it should still enjoy confidentiality. We set its frame to \(\unsealed\) rather
than \(\sealed\) to express this. Of course, some objects may be passed in place,
easily modeled by including them in \(\overline{sa}\).

\judgmentbrbr[]
             {\(\psi = \mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa}\)}
             {\(V' = V \llbracket \reg \mapsto \unsealed | \reg \in \mathit{CLR} \rrbracket
               \llbracket \reg \mapsto \public | \reg \in \overline{\reg_{args}} \rrbracket\)}
             {\(V'' = V'\llbracket \addr \mapsto \unsealed | V' ~ \addr = \object \land \addr \not \in (\mathit{passed} ~ \overline{sa} ~ \mach) \rrbracket\)}
             {\(Op ~ \mach ~ \psi ~ (V,\sigma) =
               (V',\sigma)\)}

@@

State beyond registers and memory is always considered \(\public\), and in a PIPE machine this
includes tags. That does not mean that functions should be modifying them! It just means that we
do not consider them to be part of the state being protected. It is less obvious that a function
should be prevented reading a tag, and our properties do not rule it out, although in practice
PIPE does not allow such reads. It would be quite possible to implement
the properties so that they would forbid these activities, for instance by structuring \(\mathcal{P}\)
to treat tags separately and apply stack safety to the tags on the stack, but there is no obvious
application for such a stringent property---the enforcement state must be protected in order that
enforcement not be subverted, not for its own sake.

I have a sketch of an argument that we would not gain anything meaningful from confidentiality
of tags, but it still needs some work. Still, I think it's correct not to vary the policy state.
